---
title: Daniel Roelfs, PhD
author: Daniel Roelfs, PhD
date: today
pagetitle: Daniel Roelfs' CV
format:
  html:
    include-in-header: 
        - text: |
            <link href="https://fonts.cdnfonts.com/css/cooper-hewitt" rel="stylesheet">
            <script src="https://unpkg.com/pagedjs/dist/paged.polyfill.js"></script>
            <link rel="stylesheet" type="text/css" href="css/print.css">
            <link rel="stylesheet" type="text/css" href="css/pagedjs.css" media="screen">
            <link rel="stylesheet" href="https://cdn.jsdelivr.net/npm/@tabler/icons-webfont@latest/tabler-icons.min.css">
    embed-resources: !expr (function(x) { y <- tolower(x); y == "true" })(Sys.getenv("EMBED_RESOURCES", "true"))
params:
    pdf_mode: false
execute:
    echo: false
    output: asis
    warning: false
theme:
    - css/main.scss
editor_options:
  chunk_output_type: console
---

```{r}
#| label: pkgs

library(stringr)
library(magrittr)
```

```{r}
#| label: setup

yaml_file <- yaml::read_yaml("info.yaml")

yaml_to_df <- function(yaml_file, field) {
    cols = c("item", names(yaml_file[[field]][[1]]))

    df = data.frame()
    for (item in names(yaml_file[[field]])) {
        vec = c(item)
        for (entry in cols) {
            val = yaml_file[[field]][[item]][[entry]]
            vec = c(vec, val)
        }
        names(vec) = cols
        df <- df |> dplyr::bind_rows(vec)
    }

    return(df)
}
```

::: {.socials}
```{r}
#| label: contact-info

show_email <- FALSE

yaml_to_df(yaml_file, "contact_info") %>%
    {if(show_email) dplyr::filter(., str_detect(.$item, "email|e-mail", negate = TRUE)) else .} |>
    str_glue_data("<a class='no-hover' href='{url}'><i class='ti ti-{icon}'></i></a>")

if (params$pdf_mode) {
    cat(" <span class='no-hover'>|</span> <a class='no-hover' href='https://cv.danielroelfs.com'><i class='ti ti-brand-safari'></i></a>")
} else {
    cat(" <span class='no-hover'>|</span> <a class='no-hover' href='roelfs_cv.pdf'><i class='ti ti-download'></i></a>")
}

if (show_email) {
    cat("\n
    :::: {.email}\n
    e-mail: [daniel@roelfs.net](mailto:daniel@roelfs.net)\n
    ::::\n")
    }
```
:::

## Work experience {.section}

```{r}
#| label: work-experience

yaml_to_df(yaml_file, "work_experience") |>
    str_glue_data('
    ### <<company>>

    ::: {.cv-date}\n
    <<date>>\n
    :::

    _<<position>>_

    <<description>>', .open = "<<", .close = ">>")
```

## Education {.section}

```{r}
#| label: education

yaml_to_df(yaml_file, "education") |>
    str_glue_data('
    ### <<institution>>

    ::: {.cv-date}\n
    <<date>>\n
    :::

    _<<title>>_

    <<description>>', .open = "<<", .close =">>")
```

## Skills {.section}

Daily use of Python, R, SQL (various dialects), bash, AWS, Snowflake, Git, and common packages and module. Experience also with MATLAB, LaTeX, HTML/CSS. Have previously worked with Google Cloud, SLURM.

In addition, I'm familiar with common data science and data engineering frameworks including but not limited to Shiny, Flask, Streamlit, MLFlow, Jenkins, Docker, Airflow, TensorFlow, LangChain, dbt, and various other common tools.

## Languages {.section}

```{r}
#| label: language-skills

yaml_to_df(yaml_file, "language_skills") |>
    str_glue_data('
    ::: {.skill-container}\n
    :::: {.skill-bar style="width: <<level>>%;"}\n
    <<name>> (<<cefr>>)\n
    ::::\n
    :::', .open = "<<", .close =">>")
```

## Awards {.section}

```{r}
#| label: awards

yaml_to_df(yaml_file, "awards") |>
    str_glue_data('
    ### <<name>>

    ::: {.cv-date}\n
    <<year>>\n
    :::

    _<<organisation>>_

    <<description>>', .open = "<<", .close =">>")
```

## Clincial experience {.section}

```{r}
#| label: clinical

yaml_to_df(yaml_file, "clinical") |>
    str_glue_data('
    ### <<name>>

    ::: {.cv-date}\n
    <<date>>\n
    :::

    _<<position>>_\n\n', .open = "<<", .close =">>")
```

<br>

## Commissions {.section}

```{r}
#| label: commissions

yaml_to_df(yaml_file, "commissions") |>
    str_glue_data('
    ### <<organisation>>

    ::: {.cv-date}\n
    <<date>>\n
    :::

    _<<position>>_

    <<description>>', .open = "<<", .close =">>")
```

## Portfolio {.section}

I occasionally write blogposts that serve as tutorials or showcases for how I solve certain data science problems

```{r}
#| label: portfolio

yaml_to_df(yaml_file, "portfolio") |>
    str_glue_data('
    ### [{name}]({url})

    {description}')
```

## Selected publications {.section}

```{r}
#| label: publications

str_glue(yaml_file[["publications"]][["bibliography"]])
```

For an extended list of publications, see the [publications](https://danielroelfs.com/publications) list on my website, [ORCID](https://orcid.org/0000-0002-1083-002X) or my [Google Scholar](https://scholar.google.com/citations?hl=en&user=QmVQcsAAAAAJ&view_op=list_works&sortby=pubdate) profile.

::: {.last-updated}
Last updated: `r format(Sys.Date(), "%e %B %Y")`
:::